---
title: "eds212-day5-comp1-2"
format:
  html:
    code-fold: true
    code-summary: "Show me the code"
editor: visual
execute: 
  echo: true
  warning: false 
---

```{r}
library(tidyverse)

```

# explore starwars dataset

```{r}
view(starwars, n=6)
dim(starwars)

```

this is the histogram of hist()

```{r}
hist(starwars$height)
```

this is the histogram using ggplot()

```{r}
ggplot(data = starwars, aes(x=starwars$height)) + geom_histogram()
```

```{r}

ggplot(data=starwars, aes(x=starwars$height, y=starwars$mass))+geom_point()
```
## Calculate summary statistics 

use mean() function to find means. 
Use sd() function to find standard deviations. 
```{r}
mean_height<-mean(starwars$height, na.rm=TRUE)
mean_height
```

# find and store the standard deviation of character heights 
```{r}
sd_height <- sd(starwars$height, na.rm= TRUE)
sd_height
```

# In-line reporting using code outputs 
the mean height of star wars characters is `r mean_height` with a standard deviation of `sd_height`. 

